### 2017-01-31 local-capability-machine.tex
Added missing configuration in anti-red O proof.
Some easy cases of the FTLR.

  \caption{Permission hierarchy}
  \label{fig:perm-hier}
\end{figure}
Notation:
\[
  \begin{array}{rcl}
    i       &\in& \Instrs \\
    r       &\in& \RegName\\
    \pc     &\in& \Caps \\
    \pcreg  &\in& \RegName \\
    \Phi    &\in& \ExecConfs \\
    m, \memheap&\in& \Heaps \\
    \memreg &\in& \Regs \\
    \addr   &\in& \Addrs\\
    \perm   &\in& \Perms\\
    ((\perm,\gl),\start,\addrend,\addr) &\in& \Caps \\
    n       &\in& \ints\\
    \ms     &\in& \MemSegments
  \end{array}
\]
Words and instructions:
\[
  \begin{array}{rcl}
    \lv    &::=& \refreg{r} \\
    \hv    &::=& \refheap{r}\\
    \rv    &::=& n \mid \lv \\
    i      &::=& 
                 \jmp{\lv} \mid 
                 \jnz{\lv}{\rv} \mid
                 \move{\lv}{\rv} \mid 
                 \load{\lv}{\hv} \mid 
                 \store{\hv}{\rv} \mid  \\
           &   & \plus{\lv}{\rv}{\rv} \mid 
                 \lea{\lv}{\rv} \mid 
                 \restricttwo{\lv}{\rv} \mid 
                 \subseg{\lv}{\rv}{\rv} \mid  \\
           &   & \isptr{\lv}{\rv} \mid 
                 \getp{\lv}{\lv} \mid 
                 \getl{\lv}{\lv} \mid 
                 \getb{\lv}{\lv} \mid
                 \gete{\lv}{\lv} \mid
                 \geta{\lv}{\lv} \mid \\
           &   & \fail \mid
                 \halt \mid 
  \end{array}
\]
Further define $\reg_0 \in \Regs$ such that
\[
  \forall r \in \RegName \ldotp \reg_0(r) = 0
\]

\subsection{Operational Semantics}
Assume a $\decode$ function that decodes words to instructions:
\begin{align*}
  \decode &:\Words \fun \Instrs
\end{align*}
Assume an $\encodePerm$, $\encodeLoc$, and $\encodePermPair$ function that encodes a permissions, locality, and permission pair, respectively, as an integer:
\begin{align*}
  \encodePerm &: \Perms \fun \ints \\
  \encodeLoc &: \Globals \fun \ints \\
  \encodePermPair &: (\Perms \times \Globals) \fun \ints \\
\end{align*}
Further, assume an inverse function, $\decodePermPair{}$, that decodes permissions
\[
  \decodePermPair{} : \ints \fun (\Perms \times \Globals)
\]

@@

@@

  Then $\exists W' \futurestr W$, $\hs_r$, $\hs' \ldotp$
  $\memheap[\Phi] = \hs' \uplus \hs_r \uplus \ms_f$ and $\heapSat[\hs']{n-i}{W'}$
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item By induction on $n$. In other words, assume that the theorem already
    holds for all $n' < n$.
  \item The case that $i = 0$ is impossible, since
    $(\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
    \ms_f)\neq (\halted,\Phi)$ for any $\Phi$. Assume w.l.o.g. that $i = 1+i'$
  \item 
  \end{enumproof}
\end{proof}

@@

\subsubsection{Memory Segment Satisfaction}
We expect the following lemmas to hold true:
\begin{lemma}[Downwards closure]
  \begin{align*}
    &\forall \hs, n' \leq n, W \ldotp \\
    &\quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n'}{W}
  \end{align*}
\end{lemma}

>>>>

  \caption{Permission hierarchy}
  \label{fig:perm-hier}
\end{figure}
Notation:
\[
  \begin{array}{rcl}
    i       &\in& \Instrs \\
    r       &\in& \RegName\\
    \pc     &\in& \Caps \\
    \pcreg  &\in& \RegName \\
    \Phi    &\in& \ExecConfs \\
    m, \memheap&\in& \Heaps \\
    \memreg &\in& \Regs \\
    \addr   &\in& \Addrs\\
    \perm   &\in& \Perms\\
    ((\perm,\gl),\start,\addrend,\addr) &\in& \Caps \\
    n       &\in& \ints\\
    \ms     &\in& \MemSegments
  \end{array}
\]
Words and instructions:
\[
  \begin{array}{rcl}
    \lv    &::=& \refreg{r} \\
    \hv    &::=& \refheap{r}\\
    \rv    &::=& n \mid \lv \\
    i      &::=& 
                 \jmp{\lv} \mid 
                 \jnz{\lv}{\rv} \mid
                 \move{\lv}{\rv} \mid 
                 \load{\lv}{\hv} \mid 
                 \store{\hv}{\rv} \mid  \\
           &   & \plus{\lv}{\rv}{\rv} \mid 
                 \lea{\lv}{\rv} \mid 
                 \restricttwo{\lv}{\rv} \mid 
                 \subseg{\lv}{\rv}{\rv} \mid  \\
           &   & \isptr{\lv}{\rv} \mid 
                 \getp{\lv}{\lv} \mid 
                 \getl{\lv}{\lv} \mid 
                 \getb{\lv}{\lv} \mid
                 \gete{\lv}{\lv} \mid
                 \geta{\lv}{\lv} \mid \\
           &   & \fail \mid
                 \halt 
  \end{array}
\]
Further define $\reg_0 \in \Regs$ such that
\[
  \forall r \in \RegName \ldotp \reg_0(r) = 0
\]

\subsection{Operational Semantics}
Assume a $\decode$ function that decodes words to instructions:
\begin{align*}
  \decode &:\Words \fun \Instrs
\end{align*}
\dominique{mention that it is a simplification to take decode total?}
Assume an $\encodePerm$, $\encodeLoc$, and $\encodePermPair$ function that encodes a permissions, locality, and permission pair, respectively, as an integer:
\begin{align*}
  \encodePerm &: \Perms \fun \ints \\
  \encodeLoc &: \Globals \fun \ints \\
  \encodePermPair &: (\Perms \times \Globals) \fun \ints \\
\end{align*}
Further, assume an inverse function, $\decodePermPair{}$, that decodes permissions
\[
  \decodePermPair{} : \ints \fun (\Perms \times \Globals)
\]

@@

\subsubsection{LR Sanity lemmas}

\begin{lemma}[Heap satisfaction downwards closure]
  \label{heap-sat-dc}
  \begin{align*}
    &\forall \hs, n' \leq n, W \ldotp \\
    &\quad \heapSat[\hs]{n}{W} \Rightarrow \heapSat[\hs]{n'}{W}
  \end{align*}
\end{lemma}

@@

  Then $\exists W' \futurestr W$, $\hs_r$, $\hs' \ldotp$
  $\memheap[\Phi] = \hs' \uplus \hs_r \uplus \ms_f$ and $\heapSat[\hs']{n-i}{W'}$
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item By induction on $n$. In other words, assume that the theorem already
    holds for all $n' < n$.
  \item $i \neq 0$, since
    $(\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
    \ms_f)\neq (\halted,\Phi)$ for any $\Phi$. \\
    Therefore, assume w.l.o.g. that $i = 1+i'$,
    \begin{equation*}
      (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus \ms_f) \step \var{conf'} \step[i'] (\halted,\Phi)
    \end{equation*}
  \item $\start \leq \addr \leq \addrend$, $\perm \in \{ \exec,\rwx, \rwlx \}$
    and $\var{conf'} =
    \sem{\decode(\memheap(\addr))}((\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
    \uplus \ms_f))$\\
    By definition of
    $(\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus \ms_f)
    \step \var{conf'}$, using the fact that $\var{conf'} \neq \failed$ (since it
    is not possible that $\failed \step[i'] (\halted,\Phi)$)
  \item We do a case analysis on
    $\memheap(a)$
    \begin{enumproof}
    \item Case $\memheap(a) = \jmp{\lv}$:
    \item Case $\memheap(a) = \jnz{\lv}{\rv}$:
    \item Case $\memheap(a) = \move{\lv}{\rv}$:
    \item Case $\memheap(a) = \load{\lv}{\hv}$:
    \item Case $\memheap(a) = \store{\hv}{\rv}$:
    \item Case $\memheap(a) = \plus{\lv}{\rv}{\rv}$:
    \item Case $\memheap(a) = \lea{\lv}{\rv}$:
    \item Case $\memheap(a) = \restricttwo{\lv}{\rv}$:
    \item Case $\memheap(a) = \subseg{\lv}{\rv}{\rv}$:
    \item Case $\memheap(a) = \isptr{\lv}{\rv}$:
    \item Case $\memheap(a) = \getp{\lv}{\lv}$:
    \item Case $\memheap(a) = \getl{\lv}{\lv}$:
    \item Case $\memheap(a) = \getb{\lv}{\lv}$:
    \item Case $\memheap(a) = \gete{\lv}{\lv}$:
    \item Case $\memheap(a) = \geta{\lv}{\lv}$:
    \item Case $\memheap(a) = \fail$: Contradiction, since then
      $\sem{\decode(\memheap(\addr))}((\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
      \uplus \ms_f)) = \failed$, so we have that $\failed \step[i']
      (\halted,\Phi)$ which is not possible.
    \item Case $\memheap(a) = \halt$:
    \end{enumproof}
    \begin{enumproof}
    \item
      $\sem{\decode(\memheap(\addr))}((\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
      \uplus \ms_f)) = (\halted, (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
      \uplus \ms_f))$\\
      By definition of $\sem{\cdot}$
    \item Then $i' = 0$ and $\Phi =
      (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
      \ms_f)$. Follows from $(\halted,
      (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
      \ms_f)) \step[i'] (\halted,\Phi)$
    \item For $W' = W$, $\ms_r = \emptyset$ and $\ms' = \ms$, we have that
      $\memheap[\Phi] = \hs' \uplus \hs_r \uplus \ms_f$ and
      $\heapSat[\hs']{n-1}{W'}$ (using Lemma~\ref{heap-sat-dc}).
    \end{enumproof}
  \end{enumproof}
\end{proof}

@@

\subsubsection{Memory Segment Satisfaction}
We expect the following lemmas to hold true:
